---
title: "Solution 2"
output: pdf_document
---

```{r, message = FALSE}
library(tidyverse)
library(miceadds)

df <- read.csv('https://raw.githubusercontent.com/rjblake34/waenroll/main/waenrolldf.csv', header=TRUE)
```

Run regressions
```{r, message = FALSE}
mod1 <- miceadds::glm.cluster(data=df,
                              formula = TwoYear ~ LowIncomePct + WhitePct + ELLPct + HighlyCapablePct + FemalePct +
                                TotalStudents,
                              cluster = "District",
                              family='gaussian')

mod2 <- miceadds::glm.cluster(data=df,
                              formula = FourYear ~ LowIncomePct + WhitePct + ELLPct + HighlyCapablePct + FemalePct +
                                TotalStudents,
                              cluster = "District",
                              family='gaussian')

mod3 <- miceadds::glm.cluster(data=df,
                              formula = TwoYear+FourYear ~ LowIncomePct + WhitePct + ELLPct + HighlyCapablePct + FemalePct +
                                TotalStudents,
                              cluster = "District",
                              family='gaussian')
```

Print results of model 1
```{r}
summary(mod1$glm_res)
with(summary(mod1$glm_res), 1 - deviance/null.deviance) #print r squared
```

Print results of model 2
```{r}
summary(mod2$glm_res)
with(summary(mod2$glm_res), 1 - deviance/null.deviance) #print r squared
```

Print results of model 3
```{r}
summary(mod3$glm_res)
with(summary(mod3$glm_res), 1 - deviance/null.deviance) #print r squared
```


This analysis relies on data from the Washington State Office of the Superintendent of Public Instruction (OSPI).
The panel data is created by combining datasets on college enrollment and demographics at the school district level for
each year from 2014 to 2019. The purpose of this analysis is estimate the effect of school district demographic
characteristics on college enrollment--i.e., does the makeup of a school district predict how many students choose
college after high school?

Three models are estimated in this report. Enrollment at two year, enrollment at four year, and enrollment at either are
used as the dependent variables in each model, respectively. The independent variables are rate statistics for
low income, whiteness, English language learners, highly capable, female, and district size. All variables are
calculated at the district level.

Overall, the analysis suggests districts that send more students to college tend to be higher income, less white, and
have more highly capable students. However, there are significant differences between enrollment level. Districts with
high levels of two year enrollment tend to be much whiter with much higher populations of low income students than
districts with high levels of four year enrollment. Districts with high levels of four year enrollment tend to have
many more highly capable students.

A better use for this panel data is to serve as a control for regression analysis on individual-level microdata from
ACS.

The next step for this analysis is to perform a cluster analysis to learn if there are any commonalities among school
districts with high college go-on rates, and then to incorporate ACS microdata.